Verifying Demonstrations

### 2018-02-18 paper/DB-anon-cred.tex
Adds motivation for the new DBZKPK protocol
Adds DB Schnorr protocol figure

We pointed out in \cref{DistanceBounding} that all security properties 
concerning \ac{DB} assume an \emph{honest} verifier.
This assumption does not hold in our setting, where every verifier at some point 
also might be a (malicious) prover.
We will introduce a new property for \ac{DB} protocols, the \ac{DBIV}.
Then we will propose a protocol that is \ac{DBIV}, \ac{DBMF}, \ac{DBDF}, 
\ac{DBDH} resistant but \emph{not} \ac{DBTF} resistant.

@@

@@

>>>>

We pointed out in \cref{DistanceBounding} that all security properties 
concerning \ac{DB} assume an \emph{honest} verifier.
This assumption does not hold in our setting, where every verifier at some point 
also might be a (malicious) prover.
We will introduce a new property for \ac{DB} protocols, the \ac{DBIV}.
Then we will propose a protocol that is \ac{DBIV}, \ac{DBMF}, \ac{DBDF}, 
\ac{DBDH} resistant but \emph{not} \ac{DBTF} resistant.
The protocol is based on the Schnorr identification scheme and thus allows us to 
do \ac{DB} \ac{ZKPK}, which allows us to form distance-bounding anonymous 
credentials.

@@

\NewCryptoScheme{\DBS}{DBS}
\NewAlgorithm{\DBSprove}{\DBS.\!Prove}
\NewAlgorithm{\DBSverify}{\DBS.\!Verify}

@@

We present the protocol in \cref{SchnorrFigure}.
The difference from the original Schnorr protocol is that the prover commits to 
two random values and the verifier sends two challenges.
Then the verifier decides which commitment and challenge to use in the \ac{DB} 
phase.

\begin{figure*}
  \centering
  \begin{tabular}{lcl}
    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[g, q, A]\): \\
    \toprule

    \multicolumn{3}{c}{\textbf{Setup}} \\

    \(\rho_0\rgets \Z_q, \rho_1\rgets \Z_q\)
    &
    & \\

    \(R_0\gets g^{\rho_0}, R_1\gets g^{\rho_1}\)
    & \(\ProtoSendRight{R}\)
    & \\

    % null
    & \(\ProtoSendLeft{c}\)
    & \(c_0\rgets \bin^k, c_1\rgets \bin^k\) \\

    % null
    &
    & \(b\rgets \bin\) \\

    \(s_0\gets \rho_0 + c_0\alpha\)
    &
    & \\

    \(s_1\gets \rho_1 + c_1\alpha\)
    &
    & \\

    \midrule
    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < 
        \ceil{\log_2 q}\)} \\

%    % null
%    &
%    & Random delay \\

    % null
    & \(\ProtoSendLeft{b_i}\)
    & \(b_i\gets b\), random delay \\

    \(r_i\gets s_{b_i}[i]\)
    & \(\ProtoSendRight{r_i}\)
    & \\

    \midrule
    \multicolumn{3}{c}{\textbf{Verification}} \\

    % null
    &
    & \(r = r_1|\dotsb|r_{\ceil{\log_2 q}}\) \\

    % null
    &
    & \(R_b \stackrel{?}{=} g^r A^{c_b}\) \\

    \bottomrule
  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
    \ac{DB} Schnorr protocol for \(\PK{\alpha}{A = g^\alpha}\).
    The protocol should be repeated in full to achieve the desired knowledge 
    error and distance-bounding error.
  }%
  \label{SchnorrFigure}
\end{figure*}

The intuition behind the protocol security is as follows.
The random delay in the \ac{DB} phase is important to prevent distance fraud.
Otherwise \iac{DBDF} prover could just send all bits timed to the expected 
round-trip time without waiting for the challenges.

Concerning Mafia fraud, the \ac{DBMF} adversary does not know which challenge 
the verifier will use, thus there is a \(1/2\) probability that the \ac{DBMF} 
adversary will guess it correctly.
The prover will only provide one of the responses: even if the adversary re-runs 
the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) 
will have changed --- which thus yields another \(R_b\) in the end of the 
protocol.

Distance hijacking, \ac{DBDH} \dots
